An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-05-31 poly-embed-journal/poly-embed-journal.tex
section 6 done

In a strong sonse, the trim operation reduces a loss to its core: the unique minimal set of loss vectors that drive its statistical behavior.
One can therefore think of designing consistent convex surrogates as trying to ``fill out'' this minimal set with additional loss vectors so that one attains convexity while keeping trim the same.
(At least, the above is true when restricting to minimizable losses with polyhedral Bayes risks.)

@@

\jessiet{Can someone else look this over carefully?}
We conclude this section with a similar structural result, generalizing the definition of embeddeding to properties.
We say a property $\Gamma:\simplex\toto\reals^d$ embeds a finite property $\gamma:\simplex\toto\R$ if condition (ii) of Definition~\ref{def:loss-embed} holds.
In other words, $\Gamma$ embeds $\gamma$ if we have some representative set $\Sc\subseteq\R$ for $\gamma$ and embedding $\varphi:\Sc\to\reals^d$ such that for all $s\in\Sc$ we have $\gamma_s = \Gamma_{\varphi(s)}$.
% The definitions of representative sets and embeddings naturally extend to properties.
% We say a set 
% As we define embeddings from one loss to another, one can define embeddings from one property to another, where essentially condition (i) is relaxed; see \S~\ref{app:embed-props} for a precise definition.

Roughly, our result is as follows.
First, if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
In other words, $\Gamma$ is exactly the property $\gamma$ up to relabelling reports, just with other reports filling in the gaps between the embedded reports of $\gamma$.
When working with convex surrogates, extra reports often arise in the convex hull of the embedded reports.
In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ directly elicits $\Gamma$ which embeds $\gamma$, we can almost think of $L$ as eliciting $\gamma$ itself.
Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or equivalently, if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with essentially the same level sets.
The statements about level sets make use of another corollary of Proposition~\ref{prop:embed-iff-trims-equal}, stated for properties.
\begin{corollary}\label{cor:trim-prop-red}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set.
  Then $\trimred(\Gamma)$ is the set of full-dimensional level sets of $\Gamma$.
\end{corollary}
\begin{proof}
  Let $L$ elicit $\Gamma$.
  From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}), for any finite minumum representative set $\Sc\subseteq\R$, the set $\{\Gamma_s\mid s\in\Sc\}$ is exactly the set of full-dimensional level sets $\Theta$ of $\Gamma$.
  From Proposition~\ref{prop:tfae-min-rep-nonredundant}, we have $r \in \R\setminus \red(\Gamma)$ if and only if $r$ is an element of some minimum representative set.
  As $\Gamma$ has at least one minimum representative set, we conclude $\trimred(\Gamma) = \{\Gamma_r \mid r\in \R\setminus\red(\Gamma)\} = \Theta$.  
\end{proof}

>>>>

In a strong sonse, the trim operation reduces a loss to its core: the unique minimal set of loss vectors that drive its statistical behavior.
One can therefore think of designing consistent convex surrogates as trying to ``fill out'' this minimal set with additional loss vectors so that one attains convexity while keeping trim the same.
%(At least, the above is true when restricting to minimizable losses with polyhedral Bayes risks.)

@@

We conclude this section with a structural result similar to Lemma~\ref{lem:X}, but for properties.
To do so, we must first generalize the definition of embeddeding to properties.
We say a property $\Gamma:\simplex\toto\reals^d$ embeds a finite property $\gamma:\simplex\toto\R$ if condition (ii) of Definition~\ref{def:loss-embed} holds.
In other words, $\Gamma$ embeds $\gamma$ if we have some representative set $\Sc\subseteq\R$ for $\gamma$ and embedding $\varphi:\Sc\to\reals^d$ such that for all $s\in\Sc$ we have $\gamma_s = \Gamma_{\varphi(s)}$.
% The definitions of representative sets and embeddings naturally extend to properties.
% We say a set 
% As we define embeddings from one loss to another, one can define embeddings from one property to another, where essentially condition (i) is relaxed; see \S~\ref{app:embed-props} for a precise definition.

Roughly, our result is as follows.
First, if $\Gamma$ embeds $\gamma$, the level sets of $\Gamma$ must all be redundant relative to $\gamma$.
In other words, $\Gamma$ is exactly the property $\gamma$ up to relabelling reports, but potentially with other reports ``filling in the gaps'' between the embedded reports of $\gamma$.
When working with convex surrogates, extra reports often arise in the convex hull of the embedded reports.
In this sense, we can regard embedding as only a slight departure from direct elicitation: if a loss $L$ directly elicits $\Gamma$ which embeds $\gamma$, we can almost think of $L$ as eliciting $\gamma$ itself.
Finally, we have an important converse: if $\Gamma$ has finitely many full-dimensional level sets, or equivalently, if $\trimred(\Gamma)$ is finite, then $\Gamma$ must embed some finite elicitable property with the same full-dimensional level sets.

The proof relies heavily on Lemma~\ref{lem:X}.
The statements about level sets use the following corollary of Proposition~\ref{prop:embed-iff-trims-equal} for properties.
\begin{corollary}\label{cor:trim-prop-red}
  Let $\Gamma : \simplex \toto \R$ be an elicitable property with a finite representative set.
  Then $\trimred(\Gamma)$ is the set of full-dimensional level sets of $\Gamma$.
\end{corollary}
\begin{proof}
  Let $L$ elicit $\Gamma$.
  From Lemma~\ref{lem:X}(\ref{item:X-min-Theta},\ref{item:X-full-dim}), for any finite minumum representative set $\Sc\subseteq\R$, the set $\{\Gamma_s\mid s\in\Sc\}$ is exactly the set of full-dimensional level sets $\Theta$ of $\Gamma$.
  From Proposition~\ref{prop:tfae-min-rep-nonredundant}, we have $r \in \R\setminus \red(\Gamma)$ if and only if $r$ is an element of some minimum representative set.
  As $\Gamma$ has at least one minimum representative set, we conclude $\trimred(\Gamma) = \{\Gamma_r \mid r\in \R\setminus\red(\Gamma)\} = \Theta$.  
\end{proof}
